Cover Your Basis: Comprehensive Data-Driven Characterization of the Binary Black Hole Population

### 2023-01-24 src/tex/appendicies.tex
add reproducability appendix

>>>>

\section{Reproducibility}
\label{sec:reproducibility}

In the spirit of open source and reproducible science, this study was done using the reproducibility software \href{https://github.com/showyourwork/showyourwork}{\showyourwork} \citep{Luger2021}, which leverages continuous integration to programmatically download the data from \href{https://zenodo.org/}{zenodo.org}, create the figures, and compile the manuscript. Each figure caption contains two links that point towards the dataset (stored on zenodo) used in the corresponding figure, and to the script used to make the figure (at the commit corresponding to the current build of the manuscript). The git repository associated to this study is publicly available at \url{https://github.com/bruce-edelman/CoveringYourBasis}, which allows anyone to re-build the entire manuscript. The datasets and all analysis or figure generating scripts are all stored on \href{https://zenodo.org/}{zenodo.org} at \url{https://zenodo.org/record/7566301} \citep{edelman_bruce_2022_7422514}.

### 2023-01-24 src/tex/ms.tex
add reproducability appendix

\documentclass[twocolumn,linenumbers]{aastex631}

@@

\newcommand{\msun}{\ensuremath{{\rm M}_\odot}}
\newcommand{\result}[1]{#1}
\newcommand{\bruce}[1]{\textcolor{blue}{BE: #1}}
\newcommand{\NewChange}[1]{\textcolor{green}{#1}}
\newcommand{\LinkExplainer}{The icons link to the code used to generate this figure and to \href{https://zenodo.org}{zenodo} entries of any public data used.}

@@

\section{Acknowledgements}\label{sec:acknowledments}
We thank Tom Callister, Will Farr, Maya Fishbach, Salvatore Vitale, and Jaxen Godfrey for useful discussions during the 
preparation of this manuscript and/or helpful comments on early drafts. In the spirit of open source and 
reproducible science, this paper was written using the \textsc{showyourwork} package \citep{Luger2021}, and can be 
found in this \href{https://github.com/bruce-edelman/CoveringYourBasis}{repository} and the accompanying data realease; \citet{edelman_bruce_2022_7422514}. Z.D. also acknowledges support from 
the CIERA Board of Visitors Research Professorship.  This research has made use of data, software and/or web tools obtained 
from the Gravitational Wave Open Science Center (\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the 
LIGO Scientific Collaboration and the Virgo Collaboration. The authors are grateful for computational resources 
provided by the LIGO Laboratory and supported by National Science Foundation Grants PHY-0757058 and PHY-0823459.  
This work was supported in part by the National Science Foundation under Grant PHY-2146528 and benefited from access 
to the University of Oregon high performance computer, Talapas. This material is based upon work supported in part 
by the National Science Foundation under Grant PHY-1807046 and work supported by NSF's LIGO Laboratory which is a major 
facility fully funded by the National Science Foundation.

>>>>

\documentclass[twocolumn]{aastex631}

@@

\newcommand{\msun}{\ensuremath{{\rm M}_\odot}}
\newcommand{\result}[1]{#1}
\newcommand{\bruce}[1]{\textcolor{blue}{BE: #1}}
%\newcommand{\NewChange}[1]{\textcolor{green}{#1}}
\newcommand{\NewChange}[1]{#1}
\newcommand{\LinkExplainer}{The icons link to the code used to generate this figure and to \href{https://zenodo.org}{zenodo} entries of any public data used.}

@@

\section{Acknowledgements}\label{sec:acknowledments}
We thank Tom Callister, Will Farr, Maya Fishbach, Salvatore Vitale, and Jaxen Godfrey for useful discussions during the 
preparation of this manuscript and/or helpful comments on early drafts. Z.D. also acknowledges support from 
the CIERA Board of Visitors Research Professorship.  This research has made use of data, software and/or web tools obtained 
from the Gravitational Wave Open Science Center (\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the 
LIGO Scientific Collaboration and the Virgo Collaboration. The authors are grateful for computational resources 
provided by the LIGO Laboratory and supported by National Science Foundation Grants PHY-0757058 and PHY-0823459.  
This work was supported in part by the National Science Foundation under Grant PHY-2146528 and benefited from access 
to the University of Oregon high performance computer, Talapas. This material is based upon work supported in part 
by the National Science Foundation under Grant PHY-1807046 and work supported by NSF's LIGO Laboratory which is a major 
facility fully funded by the National Science Foundation.
